\Title

### 2021-01-27 manuscript/manuscript.tex
Add data citations and more software citations

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain dataset for Southern Africa, available through the
NOAA National Centers for Environmental Information (NCEI)\footnote{
\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html}
(last accessed 25 January 2020)}.
For the synthetic airborne survey, we used a portion of the Great Britain Aeromagnetic
Survey acquired by Hunting Geology and Geophysics Ltd and Canadian Aeroservices
Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS)\footnote{
\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}
(last accessed 25 January 2020)}.
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-layouts}c).

@@

\section{Software implementation}

We have implemented the methods described in the previous sections though
a software written in Python language.
The code for generating the results of this work are available in
\url{https://doi.org/10.6084/m9.figshare.13604360} or
\url{https//github.com/compgeolab/eql-gradient-boosted}.
The gradient-boosted equivalent sources implementation is based on the
non-boosted sources available through the Harmonica library
\citep{harmonica2020}, part of the Fatiando a Terra project
\citep{fatiando2013}.
Another Python libraries were used:
Verde \citep{verde2018} to apply block reductions and managing coordinates,
Boule \citep{boule2020} for computing normal gravity,
Xarray \citep{xarray2017} and Numpy \citep{numpy2020} for managing
multidimensional datasets and numerical
computations,
Numba \citep{numba2015} for writing pre-comipled implementations and
parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures.

@@

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
The synthetic airborne survey was based upon the Great Britain aeromagnetic
data, reproduced with the permission of the British Geological Survey
\textcopyright{} UKRI.
All rights reserved.

>>>>

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain dataset for Southern Africa, available through the
NOAA National Centers for Environmental Information (NCEI).
For the synthetic airborne survey, we used a portion of the Great Britain
Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
Aeroservices Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS).
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}.
(Fig.~\ref{fig:synthetic-layouts}c).

@@

@@

\section{Data and code availability}

The Python source code used to produce all results and figures presented here
is available at
\url{https://doi.org/10.6084/m9.figshare.13604360} and
\url{https://github.com/compgeolab/eql-gradient-boosted}
under the BSD 3-clause open-source license.

The gradient-boosted equivalent sources implementation is based on the
equivalent source code in the Harmonica library \citep{harmonica2020}.
Other software used in this study includes:
Pooch \citep{pooch2020} for downloading and caching datasets,
Verde \citep{verde2018} for block reductions and coordinate manipulations,
Boule \citep{boule2020} for normal gravity calculations,
xarray \citep{xarray2017} and Numpy \citep{numpy2020} for multidimensional
arrays and numerical computations,
Numba \citep{numba2015} for just-in-time compilation and parallelization,
Matplotlib \citep{matplotlib2007} and PyGMT \citep{pygmt2020} for generating
the figures and maps,
and the Jupyter notebook programming environment \citep{jupyter2016}.
Harmonica, Boule, Pooch, and Verde are part of the Fatiando a Terra project
\citep{fatiando2013}.

All datasets used are open-access and publicly available.
The synthetic surveys were generated using
a public domain gravity dataset for Southern Africa distributed by the
NOAA NCEI (\url{https://www.ngdc.noaa.gov/mgg/gravity/gravity.html})
and the Great Britain Aeromagnetic
Survey distributed by the
British Geological Survey (BGS) under an Open Government License
(\url{https://www.bgs.ac.uk/products/geophysics/aeromagneticRegional.html}).
The shaded relief in Fig.~\ref{fig:australia} is the SRTM15+ dataset by
\citet{tozer2019}.
The Australian ground gravity
data is based on a compilation distributed by Geoscience Australia under a
Creative Commons Attribution 4.0 International Licence \citep{wynne2018}  which
was filtered and referenced to the WGS84 ellipsoid by
\citet{australia_compilation} and is distributed under the same license
(\url{https://doi.org/10.6084/m9.figshare.13643837}).

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
Contains British Geological Survey materials © UKRI.
